---
title: "A non-destructive method to quantify starch content in red clover"
author: Lea Frey, Philipp Baumann, Helge Aasen, Bruno Studer, Roland Kölliker
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# The science behind

# Technical Description

This is the code repository that produces the outputs of the manuscript with the above title.

The directory is self-contained and is designed to run reproducibly, either on your local operating system or in a Docker container. The description about how deploy this Docker image and run all analyses within this project can be found below.

# Rerun all analyses

## Reproduce the analysis on your local machine (host operating system)

First, download this repository or clone it with git.

```{bash, eval=FALSE}
git clone https://github.com/philipp-baumann/leaf-starch-spc
```

To restore all required packages at versions defined in the file [`renv.lock`](https://github.com/philipp-baumann/leaf-starch-spc/blob/master/renv.lock) based on the  [renv](https://github.com/rstudio/renv) R package, execute the following in the project directory.

```{r, eval=FALSE}
install.packages("remotes")
remotes::install_github("rstudio/renv@0.12.0")
# Automatically installs packages from CRAN and github 
# as specified in `renv.lock`
renv::restore()
```

You can manually run the scripts in sequential order, but we recommend to deploy the entire workflow in automated manner using [drake](https://books.ropensci.org/drake/) R package. This gives you tangible evidence of reproducibility.

```{r, eval=FALSE}
# Make drake plan (targets and expressions in scripts: see ./code/:
# Starts a separate R process from R for safe interactivity
source("_make.R")
```

## Reproduce the analysis in Docker container (remote server or local machine)

Docker provides an open-source solution to create an isolated software environment that captures the entire computational environment. This makes the data analysis scalable and reproducible, independent of the host operating system. To get started with Docker, there is an [rOpenSci R Docker tutorial](https://ropenscilabs.github.io/r-docker-tutorial/) that explains the motivation and basics of using Docker for reproducible research. However, you can also just follow the steps outlined below.

A `Dockerfile` is a text file that contains a recipe to build an image with a layered approach. A docker image is a running instance of a container. [This `Dockerfile`](https://github.com/philipp-baumann/leaf-starch-spc/blob/master/Dockerfile) is based on the [`rocker/rstudio:3.6.0`](https://hub.docker.com/r/rocker/rstudio/) image, which bases itself on [`rocker/r-ver`](https://hub.docker.com/r/rocker/r-ver/) with debian 9 (stretch) including version stable base R (v3.6.0) and the source build tools. The RStudio image provides RStudio server within a Docker image, that you can access via your browser. Basic instructions are given here, but for getting started you can additionally consider [this resource](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image). The image is version-stable and uses the MRAN snapshot of the last day that the R version 3.6.0 was the most recent release.

The workflow deployed here is fueled by the [`{renv}`](https://rstudio.github.io/renv/articles/renv.html) package, which manages the installation of specific package versions and sources, and the [`{drake}`](https://docs.ropensci.org/drake/) package to keep track of R code and data that produce the results.

The [drake manual lists two examples](https://ropenscilabs.github.io/drake-manual/index.html#with-docker) that combine `{drake}` workflows with Docker. This can  give you some more detail of how everything works under the hood.

### Docker recipe

The follwing steps generates the computational environments, runs all computations, and let you grab the results of the entire analysis done in R.

1. Build the docker container with instructions from the [`Dockerfile`](https://github.com/philipp-baumann/leaf-starch-spc/blob/master/Dockerfile).

```{bash, eval=FALSE}
docker build -t leaf-starch-spc .
```

2. Check wether the image is built.

```{bash, eval=FALSE}
docker images
```

3. Launch the container and share the local volume (host) with the container

```{bash, eval=FALSE}
# https://www.rocker-project.org/use/managing_users/
sudo docker run -d -p 8787:8787 -e PASSWORD=spcclover -v "${pwd}:/home/rstudio" -e USERID=$UID leaf-starch-spc
```

4.
  b. Port-forwarding: The RStudio server service running within the docker image on the remote VM can be tunneled into your local browser session using ssh port forwarding. This is extremely convenient because you one can do interactive data analysis with "local feel".

```{bash, eval=FALSE}
ssh -f -N -L 8787:localhost:8787 <your_user>@<host_ip_addres>
```


# File overview

The files in this project are organized as follows (only 2 folder levels are shown):

```{r, echo=FALSE}
fs::dir_tree(recurse = 2)
```

