---
title: "A non-destructive method to quantify starch content in red clover"
author: Lea Frey, Philipp Baumann, Helge Aasen, Bruno Studer, Roland Kölliker
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Description

This is the code repository that produces the outputs of the manuscript with the above title.

The directory is self-contained and is designed to run reproducibly, either on your local operating system or in a Docker container. The description about how deploy this Docker image and run all analyses within this project can be found below.

# Reproduce the analysis locally

## Restore packages

To restore all required packages at versions defined in the file [`renv.lock`](https://github.com/philipp-baumann/leaf-starch-spc/blob/master/renv.lock) based on the  [renv](https://github.com/rstudio/renv) R package, execute the following in the project directory:

```{r, eval=FALSE}
install.packages("remotes")
remotes::install_github("rstudio/renv@0.7.0-111")
# Automatically installs packages from CRAN and github 
# as specified in `renv.lock`
renv::restore()
```

## Rerun all analyses

You can either manually run the scripts in sequential order, or deploy the entire workflow reproducibly and automatedly using the [drake](https://books.ropensci.org/drake/) R package:

```{r, eval=FALSE}
source("00_setup-make.R")
```

## Reproduce the analysis in Docker container

A Docker image can be built as described in the file [`Dockerfile`](https://github.com/philipp-baumann/leaf-starch-spc/blob/master/Dockerfile). It bases upon the [`rocker/rstudio:3.6.1`](https://hub.docker.com/r/rocker/rstudio) image (R 3.6.1 plus RStudio), on top of which it installs system libraries for the [tidyverse](https://www.tidyverse.org/) and the [renv](https://github.com/rstudio/renv) package. Further, it automatically restores all deployed package versions, and then runs the drake plan specified in [`00_setup-make.R`](https://github.com/philipp-baumann/leaf-starch-spc/blob/master/00_setup-make.R). Henceforth, the entire analysis is reproduced in a running instance of the image (also called container).

Kindly not that the Dockerfile is not yet complete upon manuscript submission. Further instructions how to build the image, run a container instance, and retrieve the results will follow soon.

# File overview

The files in this project are organized as follows (only 2 folder levels are shown):

```{r, echo=FALSE}
fs::dir_tree(recurse = 2)
```

