---
title: "A non-destructive method to quantify starch content in red clover"
author: Lea Frey, Philipp Baumann, Helge Aasen, Bruno Studer, Roland Kölliker
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Description

This is the code repository that produces the outputs of the manuscript with the above title.

The directory is self-contained and is designed to run reproducibly, either on your local operating system or a Docker container. The description about how deploy this Docker image and run all analyses within this project can be found below.

# Reproduce the analysis

## Restore package

To restore all required packages at versions defined in the file `renv.lock`, execute the following in the project directory:

```{r, eval=FALSE}
install.packages("remotes")
remotes::install_github("rstudio/renv@0.7.0-111")
# Automatically installs packages from CRAN and github 
# as specified in `renv.lock`
renv::restore()
```

## Rerun all analyses

You can either manually run the scripts in sequential order, or deploy the entire workflow reproducibly and automated using the drake R package:

```{r, eval=FALSE}
source("00_setup-make.R")
```


# File overview

The files in this project are organized as follows (only 2 folder levels are shown):

```{r, echo=FALSE}
fs::dir_tree(recurse = 2)
```

